The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2016-07-15 paper/mri_paper.tex
added final mri sim slice to thingap paper with rms structure along z direction. could stretch these out more?

\begin{figure*}
\centering
\includegraphics[trim=6cm 4cm 6cm 3cm, scale=0.5]{stress_uy_cuts.pdf}
\caption{(Placeholder) The total stress (left) and vertical cuts of the azimuthal velocity perturbations (right). The $u_y$ perturbations shown are first order (purple), second order (orange), and total (black). The blue shaded area represents the region where the second order and total perturbations are opposing the background shear because they are negative, and the red shaded region indicates where the second order and total perturbations are opposing the background shear because they are positive.}\label{allorders_velocity}
\label{stress_uy_cuts}
\end{figure*}

@@

We conduct a full study of the MRI parameter space, focussed on the behavior with changing magnetic Prandtl number ($\mathrm{Pm} \equiv \frac{\mathrm{Rm}}{\mathrm{Re}} \equiv \frac{\nu}{\eta}$). In protoplanetary disks, as well as in liquid metal MRI experiments, the magnetic Prandtl number can be very small ($\mathrm{Pm} \sim 10^{-6}$). The scale separations caused by these large ratios of diffusivity to viscosity render the small Prandtl number regime inaccessible to simulations. Because we solve spectrally in only one dimension, rather than in two or three, our analytic formulation allows us to explore the behavior down to magnetic Prandtl numbers of $10^{-6}$ or lower.

@@

>>>>

\begin{figure*}
\centering
\includegraphics[trim=6cm 4cm 6cm 3cm, scale=0.5]{stress_uy_cuts.pdf}
\caption{(Placeholder) The total stress (left) and vertical cuts of the azimuthal velocity perturbations (right). The $u_y$ perturbations shown are first order (purple), second order (orange), and total (black). The blue shaded area represents the region where the second order and total perturbations are opposing the background shear because they are negative, and the red shaded region indicates where the second order and total perturbations are opposing the background shear because they are positive.}
\label{stress_uy_cuts}
\end{figure*}

@@

We conduct a full study of the MRI parameter space, focused on the behavior with changing magnetic Prandtl number ($\mathrm{Pm} \equiv \frac{\mathrm{Rm}}{\mathrm{Re}} \equiv \frac{\nu}{\eta}$). In protoplanetary disks, as well as in liquid metal MRI experiments, the magnetic Prandtl number can be very small ($\mathrm{Pm} \sim 10^{-6}$). The scale separations caused by these large ratios of diffusivity to viscosity render the small Prandtl number regime inaccessible to simulations. Because we solve spectrally in only one dimension, rather than in two or three, our analytic formulation allows us to explore the behavior down to magnetic Prandtl numbers of $10^{-6}$ or lower.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../figures/final_slice_MRI_run_Rm5_00e+01_eps0_00e+00_Pm1_00e-03_beta2_50e+01_Q7_50e-01_qsh1_50e+00_Omega1_00e+00_nx256_nz256_Lz10_CFL.pdf}
\caption{The final timestamp of each simulation.}\label{fig:final_slices}
\end{figure*}
